---
title: "reflectance"
author: "Guilhem Huau"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
colorlinks: true
output:
  html_document:
    self_contained: true
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: TRUE
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitStartTime <- Sys.time()
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      include = TRUE,
                      warning = TRUE,
                      message = TRUE,
                      cache = FALSE, # save chunks output
                      results = "hold", # display chunk output in one block
                      
                      # df_print paged options
                      rows.print = 10,
                      max.print = Inf,
                      
                      
                      # format
                      tidy = FALSE, # format code with 'tidy_source()'
                      tidy.opts = list(width.cutoff = 80),
                      strip.white = TRUE, #remove the white lines in the beginning or end of a source chunk
                      
                      fig.align = "center",
                      fig.width = 9,
                      fig.height = 5)
knitr::opts_knit$set(progress = TRUE,
                     verbose = FALSE,
                     width = 80)
```

```{css echo=FALSE, eval = TRUE}
/* add some CSS styling here */
```

**Packages / R-options:**
```{r pkgs_options, results='hide'}
suppressPackageStartupMessages({
  library(raster)
  library(dplyr)
  library(tidyr)
  library(plotly)
  library(ggplot2)
  library(FactoMineR)
  library(factoextra)
  library(rgdal)
  library(sf)
  library(caret)
  library(pls)
  library(glmnet)
})
#  R options
options(max.print = 20)
set.seed(16)
```



## Data import

```{r raster_data_import}
#Do not forget to download the Sentinel data in the folder src
bandB <- raster("src/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9_FRE_B2.tif")
bandG <- raster("src/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9_FRE_B3.tif")
bandR <- raster("src/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9_FRE_B4.tif")
bandNIR <- raster("src/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9_FRE_B8.tif")
bandNIR_A <- raster("src/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9_FRE_B8A.tif")
bandSWIR <- raster("src/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9/SENTINEL2B_20180920-104712-964_L2A_T31TEH_D_V1-9_FRE_B11.tif")

extent(bandR)


```


```{r crop}
test_area <- extent(503000,509000,4784000,4790000)
work_area <- readOGR("src/mygeodata")
work_area <- spTransform(work_area, crs(bandB))

bandB_crop <- crop(bandB, test_area)
bandG_crop <- crop(bandG, test_area)
bandR_crop <- crop(bandR, test_area)
bandNIR_crop <- crop(bandNIR, test_area)

writeRaster(bandB_crop, "intermediary/bandB", overwrite = T)
writeRaster(bandG_crop, "intermediary/bandG", overwrite = T)
writeRaster(bandR_crop, "intermediary/bandR", overwrite = T)
writeRaster(bandNIR_crop, "intermediary/bandNIR", overwrite = T)

```
# Indices

|                      Indices                     |           Formulas           |          Reference         |
|:------------------------------------------------:|:----------------------------:|:--------------------------:|
| SI.1   (Salinity indice 1)                       |        sqrt (red*nir)        |   Dehni and Lounis (2012)  |
| SI.2   (Salinity indice 2)                       |    sqrt (green^2 + red^2)    |   Dehni and Lounis (2012)  |
| SI.3   (Salinity indice 3)                       |      sqrt (green  x red)     |   Dehni and Lounis (2012)  |
| SI.4   (Salinity indice 4)                       |       sqrt (blue x red)      |   Dehni and Lounis (2012)  |
| SI.5   (Salinity indice 5)                       |       (red x NIR)/green      |   Dehni and Lounis (2012)  |
| SI.6   (Salinity indice 6)                       |           blue/red           |   Dehni and Lounis (2012)  |
| BI   (Brightness indice)                         |      sqrt (red^2+nir^2)      |     Khan et al. (2005)     |
| NDSI   (Normalized Difference Salinity Indice)   |    (red - nir)/(red + nir)   |     Khan et al. (2005)     |
| VSSI   (Vegetation Soil Salinity Indice)         |  2 x green – 5 * (red + nir) |   Dehni and Lounis (2012)  |
| NDVI   (Normalized Difference Vegetation Indice) |     (nir – red)/(nir+red)    |     Khan et al. (2005)     |
| SAVI   (Soil Adjusted Vegetation Indice)         | ((1+L)*nir-red))/(L+nir+red) | Alhammadi and Glenn (2008) |
| NDWI   (Normalized Difference Water Indice)      | (green - nir)/(green + nir)  |      Hanqiu Xu (2006)      |

## SI.1

```{r SI1}
SI1 <- sqrt(bandNIR_crop * bandR_crop)
SI1_data <- round(data.matrix(matrix(SI1@data@values, ncol = SI1@ncols, nrow = SI1@nrows)),3)
#plot_ly(z = SI1_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(SI1, "intermediary/SI1", overwrite = T)
```

## SI.2

```{r SI2}
SI2 <- sqrt(bandG_crop**2 * bandR_crop**2)
SI2_data <- round(data.matrix(matrix(SI2@data@values, ncol = SI2@ncols, nrow = SI2@nrows)),3)
#plot_ly(z = SI2_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(SI2, "intermediary/SI2", overwrite = T)
```

## SI.3

```{r SI3}
SI3 <- sqrt(bandR_crop * bandG_crop)
SI3_data <- round(data.matrix(matrix(SI3@data@values, ncol = SI3@ncols, nrow = SI3@nrows)),3)
#plot_ly(z = SI3_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(SI3, "intermediary/SI3", overwrite = T)
```

## SI.4

```{r SI4}
SI4 <- sqrt(bandR_crop * bandB_crop)
SI4_data <- round(data.matrix(matrix(SI4@data@values, ncol = SI4@ncols, nrow = SI4@nrows)),3)
#plot_ly(z = SI4_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(SI4, "intermediary/SI4", overwrite = T)
```

## SI.5

```{r SI5}
SI5 <- (bandR_crop * bandNIR_crop) / bandG_crop
SI5_data <- round(data.matrix(matrix(SI5@data@values, ncol = SI5@ncols, nrow = SI5@nrows)),3)
#plot_ly(z = SI5_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(SI5, "intermediary/SI5", overwrite = T)
```

## SI.6

```{r SI6}
SI6 <- bandB_crop / bandNIR_crop
SI6_data <- round(data.matrix(matrix(SI6@data@values, ncol = SI6@ncols, nrow = SI6@nrows)),3)
#plot_ly(z = SI6_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(SI6, "intermediary/SI6", overwrite = T)
```

## BI

```{r BI}
BI <- sqrt(bandNIR_crop**2 * bandR_crop**2)
BI_data <- round(data.matrix(matrix(BI@data@values, ncol = BI@ncols, nrow = BI@nrows)),3)
#plot_ly(z = BI_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(BI, "intermediary/BI", overwrite = T)
```

## NDSI

```{r NDSI}
NDSI <- (bandR_crop - bandNIR_crop) / (bandR_crop + bandNIR_crop)
NDSI_data <- round(data.matrix(matrix(NDSI@data@values, ncol = NDSI@ncols, nrow = NDSI@nrows)),3)
#plot_ly(z = NDSI_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(NDSI, "intermediary/NDSI", overwrite = T)
```

## VSSI

```{r VSSI}
VSSI <- 2*bandG_crop - 5*(bandR_crop+bandNIR_crop)
VSSI_data <- round(data.matrix(matrix(VSSI@data@values, ncol = VSSI@ncols, nrow = VSSI@nrows)),3)
#plot_ly(z = VSSI_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(VSSI, "intermediary/VSSI", overwrite = T)
```

## NDVI

```{r NDVI}
NDVI <- (bandNIR_crop - bandR_crop) / (bandNIR_crop + bandR_crop)
NDVI_data <- round(data.matrix(matrix(NDVI@data@values, ncol = NDVI@ncols, nrow = NDVI@nrows)),3)
#plot_ly(z = NDVI_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(NDVI, "intermediary/NDVI", overwrite = T)
```

## Soil Adjusted Vegetation Index

```{r SAVI}
SAVI <- (bandNIR_crop - bandR_crop) / (bandNIR_crop + bandR_crop + 0.5) * 1.5
SAVI_data <- round(data.matrix(matrix(SAVI@data@values, ncol = SAVI@ncols, nrow = SAVI@nrows)),3)
#plot_ly(z = SAVI_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(SAVI, "intermediary/SAVI", overwrite = T)
```


## NDWI

```{r NDWI}
NDWI <- (bandG_crop - bandNIR_crop) / (bandG_crop + bandNIR_crop)
SAVI_data <- round(data.matrix(matrix(SAVI@data@values, ncol = SAVI@ncols, nrow = SAVI@nrows)),3)
#plot_ly(z = SAVI_data, colors = colorRamp(c("red","green")), type = "heatmap")
writeRaster(SAVI, "intermediary/SAVI", overwrite = T)
```



# Ground data import

```{r groud_data_import}
ground_data <- read.csv("src/Données_Terrain_2018_2019(JRLv3).csv")
head(ground_data)

ground_data_small <- select(ground_data[ground_data$EC_mS_cm != "" ,c(8,10,12,30)], Coordinates_X_UTM_31, Coordinates_Y_UTM_31, Profondeur_cm, EC_mS_cm)
ground_data_small <- ground_data_small[starts_with(vars = ground_data_small$Profondeur_cm, match = "0-"),c(1,2,4)]

ground_data_small <- ground_data_small[-c(326,481,482,509,524,713,721,741),]

ground_data_small$Coordinates_X_UTM_31 <- as.numeric(gsub(",",".", ground_data_small$Coordinates_X_UTM_31))
ground_data_small$Coordinates_Y_UTM_31 <- as.numeric(gsub(",",".", ground_data_small$Coordinates_Y_UTM_31))
ground_data_small$EC_mS_cm <- as.numeric(gsub(",",".", ground_data_small$EC_mS_cm))

coordinates(ground_data_small) <- ~Coordinates_X_UTM_31+Coordinates_Y_UTM_31

ras <- raster()
extent(ras) <- extent(work_area)
crs(ras) <- crs(bandB)
res(ras) <- res(bandB)
test1 <- rasterize(x = ground_data_small, y = ras, field = 'EC_mS_cm', fun = mean)


test2 <- resample(test1, bandB_crop)
writeRaster(test2, "intermediary/ground_data", overwrite = T)
```


```{r creation_RasterStack}
ras_stack <- raster::stack("intermediary/bandB", "intermediary/bandG", "intermediary/bandR", "intermediary/bandNIR", "intermediary/SI1", "intermediary/SI2", "intermediary/SI3", "intermediary/SI4", "intermediary/SI5", "intermediary/SI6", "intermediary/BI", "intermediary/NDSI", "intermediary/VSSI", "intermediary/NDVI", "intermediary/SAVI", "intermediary/ground_data")
names(ras_stack) <- c("bandB_crop", "bandG_crop", "bandR_crop", "bandNIR_crop", "SI1", "SI2", "SI3", "SI4", "SI5", "SI6", "BI", "NDSI", "VSSI", "NDVI", "SAVI", "ground_data")
stackSave(ras_stack, "intermediary/stack")
```

```{r PCA}
ras_stack <- stackOpen("intermediary/stack")
dat <- as.data.frame(raster::extract(ras_stack, extent(ras_stack)))
colnames(dat) <- c("bandB_crop", "bandG_crop", "bandR_crop", "bandNIR_crop", "SI1", "SI2", "SI3", "SI4", "SI5", "SI6", "BI", "NDSI", "VSSI", "NDVI", "SAVI", "ground_data")

#pca_result <- PCA(dat[,-ncol(dat)], graph = F) #WARNING !!!! EVI and RVI returns some infinite number which lead to a problem

#pca_dat <- get_pca_ind(pca_result)$coord[,1:3]
#dat <- data.frame(dat, pca_dat)
dat <- filter(dat, is.na(ground_data) == F)
```

## Model lm

```{r modelLM, eval=FALSE, include=FALSE}
model <- lm(data= dat, ground_data ~ .)
summary(model)
```

## Visu data

```{r visu}
dat_visu <- dat %>%
  as_tibble()%>%
  gather(key = "variable", value = "value", -ground_data)

ggplot(dat_visu, aes(x = value, y = ground_data)) +
  geom_point() +
  facet_wrap(~variable, scales = "free")
```


```{r modeldata}
training.sample <- createDataPartition(dat$ground_data, p = 0.75, list = FALSE)
train.data <- dat[training.sample,]
test.data <- dat[-training.sample,]
```

## Model PCR

```{r modelPCR}
modelPCR <- train(ground_data~., data = train.data, method = "pcr", scale = TRUE, trControl = trainControl("cv", number = 100), tuneLength = 8) 
# Plot model RMSE vs different values of components
plot(modelPCR)
# Print the best tuning parameter ncomp that
# minimize the cross-validation error, RMSE
modelPCR$bestTune

# Summarize the final model
summary(modelPCR$finalModel)

# Make predictions
predictionsPCR <- modelPCR %>% predict(test.data)
# Model performance metrics
data.frame(
  RMSE = caret::RMSE(predictionsPCR, test.data$ground_data),
  Rsquare = caret::R2(predictionsPCR, test.data$ground_data)
)
```
## Model PLS

```{r modelPLS}
modelPLS <- train(ground_data~., data = train.data, method = "pcr", scale = TRUE, trControl = trainControl("cv", number = 100), tuneLength = 8) 
# Plot model RMSE vs different values of components
plot(modelPLS)
# Print the best tuning parameter ncomp that
# minimize the cross-validation error, RMSE
modelPLS$bestTune

# Summarize the final model
summary(modelPLS$finalModel)

# Make predictions
predictions <- modelPLS %>% predict(test.data)
# Model performance metrics
data.frame(
  RMSE = caret::RMSE(predictions, test.data$ground_data), Rsquare = caret::R2(predictions, test.data$ground_data))
```

## Model ElasticNet

```{r modelElasticNet}
model <- train(ground_data~., data = train.data, method = "glmnet", trControl = trainControl("cv", number = 100), tuneLength = 10)

# Best tuning parameter
model$bestTune

# Coefficient of the final model. You need
# to specify the best lambda
coef(model$finalModel, model$bestTune$lambda)

# Make predictions on the test data
x.test <- model.matrix(ground_data ~., test.data)[,-1]
predictions <- model %>% predict(x.test)
# Model performance metrics
data.frame(RMSE = RMSE(predictions, test.data$ground_data), Rsquare = caret::R2(predictions, test.data$ground_data))
```

# Appendix
```{r sessionInfo, echo=FALSE}
options(max.print = 10000)
cat("Document generated in:\n")
print(Sys.time() - knitStartTime)
if (Sys.info()["sysname"] == "Linux") {
  cat("\nCPU: ")
  cat(unique(system("awk -F': ' '/model name/{print $2}' /proc/cpuinfo", intern = T)))
  cat("\nMemory total size: ")
  cat(as.numeric(system("awk '/MemTotal/ {print $2}' /proc/meminfo", intern = T))*10^(-6), "GB")
  }
cat("\n\n\nSession information:\n")
print(sessionInfo(), locale = FALSE)
```